Comparison of CORD-19-trained GPT-2-based Chatbot Responses Across Different Text Semantic Similarity Approaches

### 2020-04-08 paper/paper.tex
Update repository

We used GPT-2 774M model and ran transfer learning for 2500 iterations with the
batch size of 8. We used Adam as the optimizer and set the learning rate of
0.0001. The model is available on our GitHub page.

@@

@@

We have generated over 300 answers to the questions. We have asked experienced
medical personnel at Mayo Clinic to rate our question.

>>>>

We utilized GPT-2 774M model and ran transfer learning for 2500 iterations with
the batch size of 8. We used Adam as the optimizer and set the learning rate of
0.0001. The model is available on our GitHub page.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Questions and Evaluation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Questions}

For evaluating the performance of the approaches, we have chose 12 different
questions. For each approach, we generated 5 different answers for the same
question, resulting in the total of 240 answers. We then asked experienced
medical personnel at Mayo Clinic to rate these answers. The questions are
presented below.

@@
